The Astropy Project

### 2017-11-13 main.tex
Update on Overleaf.

\documentclass[modern]{aastex61}
\usepackage{xspace}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\newcommand{\escapecmd}[1]{\texttt{\detokenize{#1}}}

@@

\begin{itemize}
   \item The goal is to produce a brief and informative paper that covers major
        \astropy principles not mentioned in the first paper, the core v2.0
        package, and infrastructure in \astropy project to support development
        in \python.
    \item We don't plan on including code in this paper, but if you think you
        will need to include code in your section, please add it to a separate
        Python module (.py file) and include it in this repository.
    \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename}
        not ``Figure''
    \item Use \escapecmd{\astropypkg} for the astropy package,
        \escapecmd{\astropy} for the astropy project, \escapecmd{\python} not
        ``Python''
    \item If your subpackage was included in Paper I, then please just include a
        note on what the package does, a reference to paper I, and any new major
        updates to your package
    \item If your subpackage was not included, then please describe the
        sub-package on level with what was in the first paper, and highlight any
        major features in it. Typical length should be equivalent to one page
        (single-column).
    \item Please make sure you are logged into Overleaf or pushing a commit with
        your information to be able to track the contributors to the paper.

@@

\section*{Global TODO items}
\begin{itemize}
    \item subpackage not sub-package!
    \item spell check!
    \item check consistent astropy usage
\end{itemize}

@@

\subsection{Coordination of Astropy}
% draft by ??
% edited by Adrian PW

@@

\subsection{Distribution packages}

\astropypkg is available from several of the Python distributions for scientific
% * <mattwcraig@gmail.com> 2017-10-27T07:13:51.093Z:
%
% > \astropypkg i
% I changed a few of the macros in here to refer to the package rather than the project because it is the package being discussed here.
%
% ^.
computing, such as Anaconda or Enthought Canopy, which include also some of
\astropy's affiliated packages.
Alternatively, \astropypkg can be readily installed from the Python Package
Index\footnote{\url{https://pypi.python.org/pypi}} (PyPI) using pip, the
recommended command-line tool for installing Python packages
that is included by default since Python 2 $\geq$ 2.7.9 and Python 3 $\geq$ 3.4.
For most recent \astropypkg releases, pre-built wheel distributions are obtainable
from PyPI for Windows, Mac OS X and Linux systems that provide faster
installation compared to the source distribution.  Optionally, the version of
the package and the dependencies needed to run or build the software are given
by a specifier to the pip package manager as described in PEP 440\footnote{For
more detailed installation instructions and optional flags see
\url{http://docs.astropy.org/en/stable/install.html\#installing-astropy}}.

@@

\section{The future of the Astropy project}
\label{sec:future}
\inlinecomment{PLL}{In addition to PY3, add some killer features that we
  plan to implement for 3.0 and beyond?}
\inlinecomment{BMS}{Some killer features we already know about to definitely
have may be mentioned here. e.g. functionality of astropy-healpix? or the
performance/speedup focus of the 3.1 release?}
\inlinecomment{BMS}{should we mention the refactored infra here?
  e.g. pytest-astropy and sphinx-astropy?}
\inlinecomment{SMC}{I've added a rough first draft -- please feel free to edit}
%\subsection{Roadmap for \python 3 only support}

Development has continued after the release of v2.0 of \package{astropy}.    The most significant development for the next release will be removing python 2 support \citep{ape10}.  While the v2.0 release is a ‘long term stable’ release (meaning that it will be supported through 2019 in both python 2 and python 3), the v3.0 \package{astropy} release will only support python 3.  This will allow the use of the new functionality in python 3, simplify the code base, and reducing the testing overhead.   The v3.0 release is currently scheduled for December 2017.

In the release cycle after v3.0, the \astropy project will focus on optimization of the code and improved documentation for the v3.1 release. To prepare for this release, software for testing and monitoring the performance of the code are being developed.   Less functionality may be introduced in this release while the focus will be primarily on improved performance.  In addition, a new suite of tutorials and documentation are being prepared for this release.

Beyond the core code, the \astropy project is also further developing the affiliated packages.  This includes elevating a suite of packages into part of the core project. While these may not be integrated into the core code, these projects provide code that is useful to the astronomical community and meet the testing and documentation standards of \astropy.   Some of these new efforts includes an initiative to develop tools for spectroscopy, integration of LSST software, and packages to support HEALPIX projection.

\subsection{Learn Astropy}
% Adrian

>>>>

\documentclass[modern]{aastex61}
\usepackage{xspace}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{ulem}
\newcommand{\escapecmd}[1]{\texttt{\detokenize{#1}}}

@@

\begin{itemize}
   \item The goal is to produce a brief and informative paper that covers major
        \astropy principles not mentioned in the first paper, the core v2.0
        package, and infrastructure in \astropy project to support development
        in \python.
    \item We don't plan on including code in this paper, but if you think you
        will need to include code in your section, please add it to a separate
        Python module (.py file) and include it in this repository.
    \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename}
        not ``Figure''
    \item Use \escapecmd{\astropypkg} for the astropy package,
        \escapecmd{\astropy} for the astropy project, \escapecmd{\python} not
        ``Python''
    \item If your subpackage was included in Paper I, then please just include a
        note on what the package does, a reference to paper I, and any new major
        updates to your package
    \item If your subpackage was not included, then please describe the
        subpackage on level with what was in the first paper, and highlight any
        major features in it. Typical length should be equivalent to one page
        (single-column).
    \item Please make sure you are logged into Overleaf or pushing a commit with
        your information to be able to track the contributors to the paper.

@@

\section*{Global TODO items}
\begin{itemize}
    \item \sout{subpackage not sub-package!} BMS: checked as done 13/11
    \item spell check!
    \item check consistent astropy usage
\end{itemize}

@@

\subsection{Coordination of Astropy}
% draft by ?? (BMS thinks Erik)
% edited by Adrian PW

@@

\subsection{Distribution of packages}

The \astropypkg core package is available from several of the Python distributions for scientific
% * <mattwcraig@gmail.com> 2017-10-27T07:13:51.093Z:
%
% > \astropypkg i
% I changed a few of the macros in here to refer to the package rather than the project because it is the package being discussed here.
%
% ^.
computing, such as Anaconda or Enthought Canopy, which include also some of
\astropy's affiliated packages.
Alternatively, \astropypkg can be readily installed from the Python Package
Index\footnote{\url{https://pypi.python.org/pypi}} (PyPI) using pip, the
recommended command-line tool for installing Python packages
that is included by default since Python 2 $\geq$ 2.7.9 and Python 3 $\geq$ 3.4.
For most recent \astropypkg releases, pre-built wheel distributions are obtainable
from PyPI for Windows, Mac OS X and Linux systems that provide faster
installation compared to the source distribution.  Optionally, the version of
the package and the dependencies needed to run or build the software are given
by a specifier to the pip package manager as described in PEP 440\footnote{For
more detailed installation instructions and optional flags see
\url{http://docs.astropy.org/en/stable/install.html\#installing-astropy}}.

@@

\section{The future of the Astropy project}
\label{sec:future}
% First draft by SMC
% edited by BMS

%\inlinecomment{PLL}{In addition to PY3, add some killer features that we
%  plan to implement for 3.0 and beyond?}
%\inlinecomment{BMS}{Some killer features we already know about to definitely
%have may be mentioned here. e.g. functionality of astropy-healpix? or the
%performance/speedup focus of the 3.1 release?}
\inlinecomment{BMS}{should we mention the refactored infra here?
  e.g. pytest-astropy and sphinx-astropy?}
%\inlinecomment{SMC}{I've added a rough first draft -- please feel free to edit}
%
\par Development has already been continued after the release of v2.0 of
\astropypkg. The most significant development for the next release will
be removing python 2 support \citep{ape10}, the v3.0 \astropypkg release
will only support python 3.  This will allow the use of the new
functionality in python 3, simplify the code base, and reducing the
testing overhead.   The v3.0 release is currently scheduled for January
2018.
%
\par In the next major release after v3.0, scheduled for the summer of 
2018, the focus will be on optimization of the code and improved 
documentation. To prepare for this release, software for testing and 
monitoring the performance of the code are being developed.   Less 
functionality may be introduced in this release while the focus will be 
primarily on improved performance.  In addition, a new suite of tutorials 
and documentation are being prepared for this release.
%
\par Beyond the core code, the \astropy project is also further 
developing the affiliated packages.  This includes elevating a suite of 
packages into part of the core project. While these may not be integrated 
into the \astropypkg core code, these projects provide code that is 
useful to the astronomical community and meet the testing and 
documentation standards of \astropy.   Some of these new efforts includes 
an initiative to develop tools for spectroscopy 
\citep[\package{specutils}, \package{specreduc}, \package{specviz}]
{ape13}, integration of LSST software, and packages to support HEALPIX 
projection% \citep{astropy-healpix}
.
\inlinecomment{BMS}{TODO: uncomment references of packages once they are available}
\subsection{Learn Astropy}
% Adrian
